coDoc: A Tool for Managing Relationships between Codes and Documents

### 2013-02-14 P4-5-page-paper/paper.tex
backup

@@

The architecture of coDoc is shown in Figure \ref{fig:architecture}. 
It contains CDT editor, poppler, PDF editor and multi-editor.
There are three kinds of data here, 1) the codes, 2) the documents, 3) the relationships.
We only handle C/C++ code at this time, 
as most system code are written in this language.
CDT editor reads and parses the codes, 
highlights syntax elements.
We use poppler to read the pdf file and render the pdf pages to images.
As poppler is developed in C++, and Eclipse RCP is in Java language,
we need a adaptor to bridge the C++ code and the Java code.
We use JNI to implement this adaptor.
PDF editor implements an adaptor, 
and use it to get the PDF page from poppler and display it.
The multi-editor is responsible to read the relationship data,
and highlight certain code piece and document piece respectively.

To represent a relationship, 
we first need to define the strategy to identify the code piece and document piece.
As

@@

\subsection{Build and Make existing code}
On the first stage of our work, we tried to make the software user-friendly. Basically, the following work is done,
\begin{enumerate}
\item Added Makefile and instructions.
\item Added accurate "usage" message to output.
\end{enumerate}

\begin{figure}
\begin{center}
\includegraphics[width=0.6\textwidth]{codoc.eps}
\caption{Structure of Dyninst}
\label{fig:codoc}
\end{center}
\end{figure}

How coDoc works is illustrated in Figure \ref{fig:codoc}\footnote{\texttt{from Bryan's paper \cite{xiao_automated_2012}}}. 
A \emph{point} is a location in a program.

\noindent \newline\textbf{Instrument Using Dyninst}\newline
\indent Figure \ref{fig:codoc} gives a general idea about how coDoc works.

The code used to achieve this goal is shown bellow,
\begin{Verbatim}[frame=single]
printf(``Hello world!'');
\end{Verbatim}

After downloading Elipse\footnote{\texttt{\url{http://www.eclipse.org}}}, we need install JDK.

To test this feature, we designed a test program. 
The functions implemented in the test program is listed in Table \ref{table:functions}.

\begin{table}[th]
\caption{Functions implemented in hello}
\centering
\begin{tabular}{rl}
\hline
Function & Description \\
\hline
fake & functioin never called \\
foo  & basic function \\
recursive & function call itself recursively \\
main & main function \\
\hline
\end{tabular}
\label{table:functions}
\end{table}

\section{Methodology and Design Decisions}
\label{sec:decision}
The result for the experiment is shown in fig.

\section{Evaluation}
\label{sec:evaluation}
The result for the experiment is shown in fig.

\section{Related Work}
\label{sec:related}
The result for the experiment is shown in fig.

% Based on what you have so far, what can you conclude?  What cool ideas did you think up but not have time to implement so far?
\section{Conclusions and Future Work}
\label{sec:conclusion}
There is still a great deal of opportunity to improve coDoc.

One way to construct the relationship for hardware related code and its documents is to use machine learning method.
This method need the seed data to train the model.

>>>>

The main contributions of this paper are list as follows,
\begin{itemize}
\item address the diffeculty of remain the integrity of the relationships when codes change
\item present a standard format for the code piece identifier
\item a standard format for the document piece identifier
\item a standard format for the relationship between the code and document
\item implement coDoc which adopts these standard formats
\end{itemize}

@@

The architecture of coDoc is shown in Figure \ref{fig:architecture}. 
It contains CDT editor, poppler, PDF editor and multi-editor.
There are three kinds of data here, 1) the codes, 2) the documents, 3) the relationships.
We only handle C/C++ code at this time, 
as most system code are written in this language.
CDT editor reads and parses the codes, 
highlights syntax elements.
We use poppler to read the pdf file and render the pdf pages to images.
As poppler is developed in C++, and Eclipse RCP is in Java language,
we need a adaptor to bridge the C++ code and the Java code.
We use JNI to implement this adaptor.
PDF editor implements an adaptor, 
and use it to get the PDF page from poppler and display it.
The multi-editor is responsible to read the relationship data,
and highlight certain code piece and document piece respectively.
To represent a relationship, 
we first need to define the strategy to identify the code piece and document piece.

\subsection{Identifying the Code Piece}
The codes are always evolving during its lifetime.
We don't want our relationships created for one version stopped working for other version.
This goal call for a robust identifying strategy for the code piece.
Our first method used to identify the code piece is to record the offset of the select code from the beginning of the code file and the selected length.
This method is straight forward and is easy to understand and implement.
However, this method definitely will violate the robust requirement.
To achieve the goal, we need to find some properties of the code that are relatively stable when code evolves.
These properties should also can serve as the key to uniquely identify the code piece.
The intuitive thought is to use the semantic information,
as it describes the intrinsical meaning of the code.
However, there is no formal method to describe this information.
We use syntax information in our approach to form the main element of our identifier.
The code can be parsed and represented by a syntax tree.
The change of the code in one branch will usually not affect the code branch in the other.
If we can identify the code piece based on the position in the syntax tree,
we can design a robust method to identify the code piece.
To make the method more robust,
we can introduce the information in the first method as the second key.
When the syntax identifier fails to locate the code piece,
we can use the offset information to assited the decision.
We also include in the identifier the content for the integrity check.
The structure used to achieve this goal is shown bellow,
\begin{Verbatim}[frame=single]
class CodeSelection {
  private String syntaxcodepath;
  private String selcodepath;
  private String syntaxcodetext;
  private String selcodetext;
}
\end{Verbatim}

\section{Methodology and Design Decisions}
\label{sec:decision}
\subsection{Embedded vs Seperate for PDF Reader}
The tool should display both codes and documents at the same time.
We can implement the code viewer and the PDF viewer in seperate process,
and use inner process communication (IPC) techniques to synchronize.
The advantage of this method is that each windows is in their own window,
can ocuppy the whole screen,
and display more content which eliminate the need to scroll the window horizontally.
When the user uses a computer with dual monitor,
the tool implementing this method is extremely a good choice,
as the user can choose to display the code and the document in seperate moniter.
However, this implementation is heavy,
and get performance issues.
When using the tool, 
the user may need to launch the PDF reader,
which is slow.
Our earlier implementation use this method,
and encountered a lot of synchronization problems oriatated from the IPC communication.
In coDoc, we choose to implement the code viewer and the code viewer in the same process.
This way, all the commucations are done in the same process.
%The Eclipse framework even makes the whole system single thread.
No IPC communication is needed,
which is more efficient and makes the tool more user-friendly.
With the new method, we can smoothly operate the tool without any uncomfortable feeling.
The advantage of the first method come the disadvantage of the new method,
as the code viwer and the document viwer should share the whole screen now.
However, with a efficient and user-friendly screen split strategy and screen area assignment method,
we can make the user feel less uncomfortable when viewing the content.
Also, most programmer now not only are using dual moniters, 
but also the moniters they are using are larger and larger.
Using a larger moniter with high definition will make this disadvantage point nothing.
And even better, in this situation, this method will overcome the first method,
as moving the eyes between two big moniter is energy consuming.

\subsection{Relationship Store Model}
In coDoc, we store the relationship data in XML file, 
instead of the SQL database.
The reason that we didn't use a SQL database is that the relationships is semi-structured,
as we decide to store the content along with the identifier.
The content is used to further check the integrity.
XML database is very suitable for our semi-structured data here.

\section{Evaluation}
\label{sec:evaluation}
\textbf{Effectiveness.} We have evaluated coDoc by mapping two virtual devices and their related document.
The number of relationships created and the time used to created these relationships is listed in Table \ref{table:evaluate}.

\begin{table}[th]
\caption{Evaluate Result}
\centering
\begin{tabular}{rcc}
\hline
Code & \# of Relationships & time(hr) \\
\hline
dio & 108 & 2 \\
e100  & 213 & 4\\
\hline
\end{tabular}
\label{table:evaluate}
\end{table}

The fine granularity of the identifying method makes the relationship results very accurate, 
80\% of the code piece are marked inside the statement.
This result is hard for comment based method to achieve.
The same result happens for the document.
In the whole relationships, 
90\% of the document pieces are marked as on cell in a table.
The comments in the PDF file will be too crowd to be useful,
as it will affect the normal reading of the document.
Our approach can also make the development efficient,
as we don't need the developer to change both the code and the document when only relationship is created.
This makes the code and document neat and easily to read and understand,
and will them be understand effeciently.

\noindent \textbf{Usability.} We implement coDoc as an Elipse\footnote{\texttt{\url{http://www.eclipse.org}}} Rich Client Program (RCP), 
which can make our tool share the user style with Elipse that is acustomed by many programmer.
Figure \ref{fig:platformview} is the screenshot of the tool.
Three persons with no exprience with coDoc before have successfully use this tool to created the relationships for their codes and documents.
They didn't find any difficulties when using this tool.
All the feedbacks are positive regarding to the use of the tool.
Now they can easily create their relationships by selecting the code and document piece using mouse, input the comment using keyboard.
They can also manage the relationships by sorting by attributes, search certain relationships by keywords.
They also find the feature that allow to categorize the relationships helpful,
as it makes the relationships more neat when the number of relationships is large.

In our own experience, we found that the ability to see the codes, 
the documents and the relationships in the same screen really saves a lot of time,
as we don't need to switch between different softwares.
The visualized interface also saved us time to learn the detailed syntax about the identifier formats,
and to write the identifier manually.
We believe this tool will lead to increased productivity.

@@

\section{Related Work}
\label{sec:related}
Current tools can manage codes. 
These kinds of tools include revision control software like git, svn. 
Revision tools can give the evolving history of the software.
These tools usually adopt text comparation tools to figure out the differences between the versions of the software.
The comparation tools can easily give the result about the match points and mismatch points in the codes,
which means they can manage the relationships between different versions of codes.
However, these tools are not designed to manage documents.
Though some people also use them to manage documents,
they only use it as a persistent data warehouse.
They can not take the advantages of the comparation tools, 
as these tool usually can only cope with text file.
People are using code comments to record the related document piece.
However, no consistent format exists,
which makes these information not managable,
especially when these comments are made by many different developers.

Full text indexing system is developed to processing documents.
However, they can only relate the keyword to certain documents.
They do not deal with both codes and documents. 
Like full text indexing system,
search engines also work with documents in similar way.
Most of the documents that are dealed by search engines are web pages.
Many PDF readers can support highlighting and commenting.
With these features, we can relate a document piece to a code piece.
However, these links created are not stable,
and the PDF readers can not check the integrity of these information.

Generally speaking, these are tools can either handle code management or document management.
However, they are not designed to do both,
and managing the mixture of codes and documents is definitely a mission impossible task for them.

% Based on what you have so far, what can you conclude?  What cool ideas did you think up but not have time to implement so far?
\section{Conclusions and Future Work}
\label{sec:conclusion}
We implement coDoc, 
a tool to managing the relationships between the hardware related codes and their documents.
The main contributions in this paper are the method to identify the code piece.
Our experiences of using coDoc to manage two virtual device codes and their documents show the tool is robust and efficent,
and is helpful when developing the virtual devices.
It can remain stable respect to the evolution of the codes.

There is still a great deal of opportunity to improve coDoc, 
\begin{enumerate}
\item combine it with revision control tools to provide a more user-friendly tool suit for developing and maitaining the codes while managing the documents at the same time.
\item more robust method to identify the document piece in the PDF document to make the tool invariant to the change of the document.
\item one way to construct the relationship for hardware related code and its documents is to use machine learning method.
This method need the seed data to train the model.
\end{enumerate}
